%!TEX root = /Users/andreasmller/Documents/DTU/Computerspil/scienceman/report/report.tex
\section{In the name of science} % (fold)
In the game you play a scientist who works on a top secret project for a large private corporation. In his work he has developed a pair of gloves, that grands the user various telekinetic abilities.
    When our hero discovers that the corporation he works for plans to use his inventions for various evil deeds, he steals the gadgets, and embarks on a journey to destroy the evil corporation.

The game has two types of characters:
	The hero, who will be unarmed, but equipped with the powergloves.
	The bad guys, consisting of the evil corporations security personel, who will be armed with various weapons, and will try to stop the hero at all cost. 
	Besides from the characters the levels will be populated by a large amount of inanimate objects which both serves as obstacles for the player to pass, and weapons to defeat the bad guys.
	
	
	
     

\subsection{Game rules} % (fold)

The purpose of the game is to eliminate the bad guys and escape the facility.

The hero defeats his opponents by causing a collision between an enemy and an object. This can either be done by accelerating an object into an enemy, or an enemy into an object. The enemy will take damage based on the impact of the collision. Each enemy has a certain amount of health, and each impact will do damage based on the impulse of the impact.
The hero can manipulate objects by using the powers of his powergloves.
\begin{itemize}
	\item PUSH! Push enemies and object away from you with great force causing great damage upon collision.
	\item PULL! Pull objects or enemies towards you.
	\item GRAVITY WELL! The gravity well creates a point in front of the hero with a high gravitational pull. The gravity well pulls nearby objects towards it to create a cluster, which can be used as a shield, or pushed towards an opponent. The gravity well can only be maintained for a short while, and causes the gloves to heat up very quickly.
	\item SLOW! The hero can slow down time, giving him super fast reactions.       	
\end{itemize}

There will be several kinds of enemies trying to stop the player from escaping. 
Some enemies will have ranged weapons and shoot at the player, and some will be armed with melee weapons, and try to attack the player up close. The different enemies, and different combination of enemies will force the player to use different strategies. Hiding behind a couple of crates might work great against a ranged attacker, but the melee enemies will be able to get past them and attack you.

The hero has a health bar which shows how much damage he has taken. The different types of attacks, from the different enemies cause different amounts of damage.

	Each level is divided into sections, and after each section a portion of the heroes health will regenerate. 

	Upon death the hero will return to the start of the section with full health. This way the game player will not continuously be punished by entering a section while low on health.
	
	Heat is generated when the hero uses his gadgets. This is serves as a way to limit his abilities. If his gadgets overheat, they will become temporarily disabled, until they cool down to safe levels.


\subsection{Desired features} % (fold)
desired features

 The game centers around the use of the 2d physics engine, and the ability to use the various objects in a level as weapons. The main features of  the game is therefore the abilities, granted by the powergloves, to manipulate objects.  These abilities must function smoothly, as they are the foundation of almost all aspects of the game.

\paragraph{Puzzles} % (fold)
Besides the combat , the game should include a number of different puzzles that requires the abilities of the powergloves to solve. These can range from obstacles that need to be moved, to ledges that can only be reached by piling crates, or hidden doors that are opened by the PULL! power.

\paragraph{Bossevents} % (fold)
At the end of each level should be a boss event. This can either be a specifik kind of enemy, with a large amount of hitpoints, and special weaponry, or a large scale puzzle, that requires the use of all the heroes abilities to complete.

 
\paragraph{HUD} % (fold)
The game should have a heads up display, that shows the players hitpoints, game score, and boss hit points during a boss fight.


